---
title             : "Top-down moderators on generic understanding"
shorttitle        : "Top-down moderators on generic understanding"

author: 
  - name          : "Michael Henry Tessler"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "450 Serra Mall, Bldg. 420, Rm. 316, Stanford, CA 94305"
    email         : "mhtessler@stanford.edu"
  - name          : "Noah D. Goodman"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Department of Psychology, Stanford University"
    
header-includes:
  - \usepackage{tabularx}
  - \usepackage{multicol}
  - \usepackage{wrapfig}
  - \usepackage{caption}
  - \usepackage{booktabs}
  - \usepackage{amsmath}
  - \usepackage{graphicx}
  - \usepackage{subcaption}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  
author_note: >
  This manuscript is currently in prep. Comments or suggestions should be directed to MH Tessler.

abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["generics.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no

class             : "man"
output            : papaja::apa6_pdf
---
\newcommand{\denote}[1]{\mbox{ $[\![ #1 ]\!]$}}
\newcommand*\diff{\mathop{}\!\mathrm{d}}
\definecolor{Red}{RGB}{255,0,0}
\definecolor{Green}{RGB}{10,200,100}
\definecolor{Blue}{RGB}{10,100,200}

\newcommand{\mht}[1]{{\textcolor{Blue}{[mht: #1]}}}
\newcommand{\ndg}[1]{{\textcolor{Green}{[ndg: #1]}}}
\newcommand{\red}[1]{{\textcolor{Red}{#1}}}


```{r load_packages, include = FALSE}
library(papaja)
library(tidyverse)
library(cowplot)
library(ggthemes)
library(RColorBrewer)
library(ggpirate)
theme_set(theme_few())
```

```{r analysis_preferences}
# Seed for random number generation
set.seed(42)
```


# Introduction


<!-- Include (in the GD) some information analysis of Cimpian, Gelman, & Brandone (2010), Lang Cogn Process -->

In the literature on generics, it is long argued that generic meaning cannot be reduced to probabilities or quantification [@Carlson1977; @Carlson1995; @Gelman2007; @Leslie2008; @Prasada2000; @Cimpian2010theory; @Cimpian2010].
As I argued in the introduction, these studies (both empirical and theoretical) are limited by their assumption that the literal meaning of generics is directly inspectable, that we can interpret our intuitions or findings about generics without needing to formalize the background knowledge that any language user would be bring to interpret a sentence.
In this chapter, I examine a few of these studies to see, if indeed, they are incompatible with a prevalence-based semantics. 

I will examine two case studies that show top-down influence of conceptual knowledge on generic endorsement: the origins and dangerousness of properties.
An old intuition with generics is that at least some generics express properties that are especially enduring and central to a category [@Lyons1977]. 
This intuition was elaborated into a notion of a "principled connection" between a kind and a property [@Prasada2006], which support both a normative expectation (e.g., *Ks should F*) and explanation of category membership (e.g., *x is a K because it Fs*).
@Gelman2007 posit that the way in which an exemplar comes to have a property---the *origins* of a property---can bring about a principled connection between the kind and the property. 
Learning that individuals are born with the property (*intrinsic origins*) signals that the kind has a principled connection to the property, whereas observing individuals who acquire the property from the external world (*extrinsic origins*) is less likely to bring about a principled connection. 

Further evidence of how our understanding of generics is tied to our conceptual knowledge comes from the observation that properties that are "striking, appalling, or otherwise gripping" make the generic "...more tolerant [...] to exceptions" [@Leslie2008; p.15].
This argument comes from intuitions to explain why sentences like "Mosquitos carry malaria" and "Tigers eat people" sound like true generic sentences despite the prevalence of the feature in the referent categories being exceptionally low. 
@Cimpian2010 provided some empirical support for this claim using generics about novel categories (e.g., "Lorches have dangerous purple feathers"). 
Information about dangerousness was found to increase participants' propensity to endorse generic sentences when information about the referent prevalence was fixed (e.g., when 30% of lorches have these purple feathers) [@Cimpian2010, Expts. 1 & 4]. 

Both @Gelman2007 and @Cimpian2010 have participants judge whether or not they agree with generic sentences (or if they would rate them as "true" vs. "false").
From the preceding chapters, we know that endorsement depends on the referent prevalence (i.e., the prevalence of the property within the referent category) in a nonlinear, relative way that depends on the distribution of prevalence of the property within a set of relevant alternative categories. 
Thus, the minimal computational model presented here already has two distinct avenues by which theory-based expectations can influence endorsement: the prevalence prior and the referent prevalence.
Prevalence prior distributions reflect complex structure (often manifesting as multi-modal distributions) and can change dramatically between properties of different types (e.g., biological vs. accidental properties; Ch. 2, Expt. 1; Ch. 3, Expt. 1, Expt. 2) and even within properties that are all of the same conceptual type (e.g., biological properties; Ch. 2, Expt. 2l Ch. 3, Expt. 2). 
Second, referent prevalence is not the objective frequency of the property among actual members of the category in the world. 
Instead, we define prevalence as a subjective, predictive probability that exists in the mind of the speaker.
(Frequency information is relevant insofar as it informs a speaker's beliefs about the property or event's probability of occurring in the future.)
In our experiments on habitual endorsement (Ch. 3, Expt. 2c), we showed how endorsement patterns can easily be divorced from the objective, present frequency, even taking into account the prior distribution over prevalence.
In those experiments, what mattered for endorsement was participants' predictions about the future (though again, in a manner relative to the prevalence prior). 

We revisit the effects of property origins and property dangerousness through the lens of the computational model.
First, if referent prevalence is what matters for generic endorsement, then the "pricipled connections" thought to result from learning intrinsic property origins in @Gelman2007 would matter only insofar as it increases the subjective probability that a future instance of the category would have the property. 
Second, if information about dangerousness is argued to influence generic endorsement in a way independent of prevalence, then it must be shown that information about dangerousness does not alter the prevalence prior.
We test these arguments in this chapter.

# Experiment 1: Property origins

So far, we have shown that property prevalence is sufficient to formalize the semantics of generic statements as an underspecified scalar denotation.
But what is property prevalence?
If generic language is truly conveying generalizations, it would be useful for it to reflect expectations, not just the current statistics in the world.
The current frequency of a property is often a good indicator of future frequency, yet statistics can be distorted by spurious events.
The causal history of a property may be more or less important for implying the property will be present in future situations.
Does generic language communicate prevalence in terms of past frequency or future expectations?

To answer this, we adopt an experimental paradigm used by @Gelman2007 to show that generic language is sensitive to theory-based considerations.
In the original paradigm, participants are told a story about a novel creature (e.g., dobles) and a property of that kind (e.g., have claws).
Participants are then either told that the creature was born with the property or that it acquired the property through extrinsic means (e.g., by finding claws and putting them on). 
Then, participants are told about an event that either causes the property to disappear (e.g., they drank a chemical and their claws fell off) or that leaves the property intact, and are asked whether or not the generic (e.g., "Dobles have claws") applies.
The original finding was that adult judgments were sensitive to the origins of the property (i.e., born vs. acquired), and insensitive to the outcome of the event (i.e., property maintained vs. lost): Participants fully-endorsed the generic when it was inborn, and rejected it when it was acquired, regardless of the current prevalence of the property.

In Experiment 3a, we use the same basic paradigm to measure *predictive prevalence*: participants' expectations about future instances of the kind.
We explore the predictions of our truth judgments model, assuming that *predictive prevalence* is what is being communicated.
In Experiment 3b, we use a truth judgment task similar to @Gelman2007 and compare participants' judgments to the model's predicted endorsements.

## Experiment 1a: Predictive Prevalence Elicitation

The design of this experiment is based on a study reported in @Gelman2007 with some slight modification.
The original study was done on 14 undergraduates.

### Method

#### Participants

We recruited 80 participants over MTurk.  
The experiment took about 3 minutes and participants were compensated \$0.35.

#### Procedure and materials

On each trial, participants read a vignette about a novel creature. For instance,

> These are dobles. [picture of ten dobles with claws] Here is how they grew. They grew up with claws. First they were born, then they got bigger, then they were full size. [picture of a doble with claws, getting bigger and bigger; in some vignettes, the animal was first shown hatching out of an egg with the relevant property already visible] Then one day they drank a bad chemical. They got very sick and this is how they looked. [picture of ten dobles without claws]

The trial proceeded by participants reading the text, and clicking a button to continue to the next part of the story (at which time, the images changed according to the example above).

Participants saw four trials: two in which the creatures are born with the property (*intrinsic origins*) and two in which the creatures are shown discovering and acquiring the property (*extrinsic origins* e.g., painting themselves brown).
This was crossed with either the creatures drinking a "bad chemical" and losing the property, or drinking a "yummy drink" and maintaining the property.
The outcome of this event determined the final presentation of images that the participant saw (e.g., either ten dobles with claws or ten without).

With the final display of dobles present (either property lost or maintained), we measured *predictive prevalence* by telling participants: "A new doble was born today. When it becomes full grown, how likely is it that it would have claws?"
Participants responded using sliders ranging from "very unlikely" to "very likely".

We used two different types of properties: colors (e.g., "Dobles are green.") and body parts (e.g., "Dobles have claws.").
For each type of property, there were approximately eight different exemplars (different colors or different body parts for different creatures).
The creatures were either birds, bugs, or fish, with randomly sampled physical dimensions (e.g., sizes of body or tail).
The experiment in full can be viewed at \url{http://stanford.edu/~mtessler/generics/experiments/predictive/predictive-elicitation-1-elicitation.html}.

### Results and truth judgment predictions

The average predicted prevalences for the four experimental conditions are shown in Table \ref{tab:predictive}.
We observe a main effect of origins, such that when participants read that the creatures had the property from birth, future creatures  are much more likely to have the property as compared to when the property is acquired.
We see that, in our paradigm, participants are also sensitive to the outcome of the event  (property lost or maintained). 
This is surprising given @Gelman2007's reporting of no effect of the event outcome on endorsement.
When participants observe a creature who loses the property by drinking a chemical, they report future members of the category are less likely to have the property.
This inference could be driven by inferences about the property (e.g., learning that the property is an unstable property because you can lose it simply by drinking something) or by inferences about the event (e.g., learning that the "chemical drinking" event is within the space of possibilities for dobles, and thus it could happen in the future).

\begin{table}
\centering
\begin{tabular}{l|l|r|r|r}
\hline
Origins & Event Outcome & Collapsed Mean [95\% CI]  & Color  [95\% CI] & Body Part [95\% CI] \\
\hline
Extrinsic & Lost  & 0.15 [0.10, 0.21]& 0.13 [0.07, 0.21] & 0.17 [0.09, 0.26] \\
\hline
Extrinsic & Maintained & 0.32 [0.24, 0.39] & 0.24 [0.16, 0.35] & 0.38 [0.27, 0.50] \\
\hline
Intrinsic & Lost  & 0.69 [0.62, 0.76] & 0.73 [0.63, 0.83] & 0.66 [0.56, 0.75] \\
\hline
Intrinsic & Maintained  &0.95 [0.94, 0.97] & 0.96 [0.94, 0.98] & 0.94 [0.91, 0.97] \\
\hline
\end{tabular}
\caption{Predicted prevalence for the four experimental conditions of Expt.~3a. Right two columns show the summaries broken down by the two types of properties used in the experiment.}
\label{tab:predictive}
\end{table}

We use these predicted probabilities as the prevalence $p$ that the speaker model is trying to communicate: $S(u\mid p)$, and examine the model's predicted truth judgments.
We explore the model's predictions for each origin and event outcome, as well as when the data is split by property type (color vs. body parts). 
For priors $P(p)$, we use the body part and color priors elicited in Ch. 2., Expt. 1a.
We see that the model predictions track closely the predicted prevalence (Figure \ref{fig:dobles}a, top, compare with predicted prevalence in Table \ref{tab:predictive}).
This is because both color and body part priors are relatively broad, and hence when the property is (predicted to be) more prevalent, the generic has a higher probability of applying (see schematic predictions from Figure \ref{fig:schematic-unif} ``have wings'' for comparison).
We also see that the model predicts a subtle by-item difference, such that the influence of the event outcome (lost or maintained) on generic endorsement is predicted to be stronger for body parts than for color terms (Figure \ref{fig:dobles}a, bottom).
This prediction is mostly due to the predicted prevalence for the conflict conditions (intrinsic-lost and extrinsic-maintained) being subtly different (Table \ref{tab:predictive}, right-most columns).

The model thus makes two novel predictions for generic endorsement in the paradigm by @Gelman2007.
We predict that in addition to the main effect of origins, we should see a second main effect of event outcome.
Second, we predict that this effect should be slightly stronger in the case of color properties than in the case of body part properties.

## Experiment 1b: Truth Judgment Task

In this experiment, we test the predictions of our model using a truth judgment measure in the same paradigm.

### Method

#### Participants

We recruited 80 participants over MTurk.  
The experiment took about 3 minutes and participants were compensated \$0.35.
None of the participants completed Expt. 1a as well.

#### Procedure and materials

The procedure and materials are exactly the same as in Expt. 1a, with the exception of the dependent measure.
After reading each vignette, participants were asked: "Do you agree or disagree that: *generic statement* (e.g., Dobles have claws)".
Participants responded by choosing one of two radio buttons corresponding to agree or disagree.

#### Results and discussion

<!-- %                                         Estimate Std. Error z value        Pr(>|z|)     -->
<!-- %(Intercept)                               -2.9444     0.5130  -5.740 0.0000000094624 *** -->
<!-- %event_outcomemaintained                    2.6931     0.5603   4.807 0.0000015342262 *** -->
<!-- %originsintrinsic                           3.6753     0.5658   6.496 0.0000000000824 *** -->
<!-- %event_outcomemaintained:originsintrinsic   0.2396     0.9400   0.255           0.799     -->

Our pragmatics model with the elicited predicted prevalence from Expt. 1a made two novel predictions for this experiment: (1) in addition to a main effect of origins, we would find a main effect of event outcome; (2) this effect would be stronger for body part properties than for color properties.
As predicted, we found two main effects (Figure \ref{fig:dobles}b, top).
The main effect of property origins replicated ($\beta=3.6, SE=0.57, z=6.5, p<1\text{e}10$): participants were more likely to endorse the generic when it was about a property that the creature was born with.
In addition, we find a second main effect of event outcome 
 ($\beta = 2.69, SE = 0.56, z=4.8, p<1\text{e}5$): participants were more likely to endorse the generic when the property was maintained than when it was lost.
 
The fact that we find a second main effect of event outcome in addition to origins, whereas the original only found a main effect of origins, makes it worth noting the differences between our paradigm and the original study by [@Gelman2007].
In the original study, the first sentence of each vignette used the possessive "my": "These are my dobles.".
At the end of each vignette, the original study had participants judge two statements in counterbalanced order: "Do my dobles have claws?" and "Do dobles have claws?"
Finally, the original sample size was 14; ours was 80. 
To see whether this second main effect could be attributed to a subgroup of participants making their judgments based only on the final screen (which showed creatures with or without the property, depending on the event outcome), we classified each participant according to their pattern of responses. 
Just as many participants endorsed the generic based on the final screen alone (*Only outcome*: 19) as there were basing their endorsement on both the outcome and the origins (*Both outcome and origins*: 16).
36 participants based their responses on only the origins, and 9 participants exhibited some other pattern of responses.
Thus, it seems this effect is not due to a subgroup of participants basing their responses on only the final screen.

\begin{table}[]
\centering
\begin{tabular}{@{}lllll@{}}
\toprule
  & Only origins & Only outcome & Both & Neither \\ \midrule
n & 36           & 19           & 16   & 9       \\ \bottomrule
\end{tabular}
\caption{Numbers of participants ($N=80$) who made their generic endorsement based on different factors.}
\label{tab:dobles}
\end{table}


When we break down the results by item, we see that this effect is stronger for body part properties than for color properties (Figure \ref{fig:dobles}b, bottom).
The endorsement of a generic for color properties (e.g., "Lorches are green") seems to be less sensitive to the outcome of the event (i.e. Lorches losing their color as a result of drinking a chemical).
This may be due to participants' intuitive theories of properties and their stability (skin color is more stable than body parts like feathers).
Indeed this difference is apparent in the predictive prevalence task (Expt. 1a).
For the 8 data points of generic endorsement based on origins, outcome, and property type, our model's predictions match the data well ($r^2(8) = 0.96$).
We, thus, elaborate our theory:
The semantics of generics can be understood as a threshold on property prevalence, and this prevalence is a speaker's subjective belief about what is likely to be the case in the future.

\begin{figure*}
\begin{tabular}{l l}
(a) $S_2$ model predictions & (b) Human endorsement of generic statements \\
\\
\centering
    \includegraphics[width=0.5\columnwidth]{dobles-model.pdf} & 
        \includegraphics[width=0.5\columnwidth]{dobles-results.pdf} \\
      \includegraphics[width=0.5\columnwidth]{dobles-model-byItem.pdf} & 
      \includegraphics[width=0.5\columnwidth]{dobles-byItem-results.pdf} \\

\end{tabular}
    \caption{
    Prevalence is a predictive probability.
    (a) Truth judgment model predictions given the predicted prevalence elicited in Expt.~3a.
    (b) Average endorsement of the generic statement in Expt.~3b (replication of Gelman and Bloom, 2007).  
    Bottom row shows data and predictions broken down by property type.
  }
  \label{fig:dobles}
\end{figure*}


# Experiment 2: The impact of dangerousness

# Experiment 3: Transient properties

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
