---
title             : "Top-down moderators on generic understanding"
shorttitle        : "Top-down moderators on generic understanding"

author: 
  - name          : "Michael Henry Tessler"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "450 Serra Mall, Bldg. 420, Rm. 316, Stanford, CA 94305"
    email         : "mhtessler@stanford.edu"
  - name          : "Noah D. Goodman"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Department of Psychology, Stanford University"
    
header-includes:
  - \usepackage{tabularx}
  - \usepackage{multicol}
  - \usepackage{wrapfig}
  - \usepackage{caption}
  - \usepackage{booktabs}
  - \usepackage{amsmath}
  - \usepackage{graphicx}
  - \usepackage{subcaption}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  
author_note: >
  This manuscript is currently in prep. Comments or suggestions should be directed to MH Tessler.

abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["generics.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no

class             : "man"
output            : papaja::apa6_pdf
---
\newcommand{\denote}[1]{\mbox{ $[\![ #1 ]\!]$}}
\newcommand*\diff{\mathop{}\!\mathrm{d}}
\definecolor{Red}{RGB}{255,0,0}
\definecolor{Green}{RGB}{10,200,100}
\definecolor{Blue}{RGB}{10,100,200}

\newcommand{\mht}[1]{{\textcolor{Blue}{[mht: #1]}}}
\newcommand{\ndg}[1]{{\textcolor{Green}{[ndg: #1]}}}
\newcommand{\red}[1]{{\textcolor{Red}{#1}}}


```{r load_packages, include = FALSE}
library(papaja)
library(tidyverse)
library(cowplot)
library(ggthemes)
library(RColorBrewer)
library(ggpirate)
theme_set(theme_few())
```

```{r analysis_preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, cache=T, message=FALSE, sanitize = T)
```


# Introduction


<!-- Include (in the GD) some informal analysis of Cimpian, Gelman, & Brandone (2010), Lang Cogn Process -->

In the literature on generics, it is long argued that generic meaning cannot be reduced to probabilities or quantification [@Carlson1977; @Carlson1995; @Gelman2007; @Leslie2008; @Prasada2000; @Cimpian2010theory; @Cimpian2010].
These studies (both empirical and theoretical) are limited by their assumption that the literal meaning of generics is directly inspectable, that we can interpret our intuitions or findings about generics without needing to formalize the world knowledge that any language user would be bring to interpret a sentence.
In this chapter, I examine a few of these studies to see, if indeed, they are incompatible with a probability-based semantics. 

I will examine two case studies that demonstrate top-down influence of conceptual knowledge on generic endorsement: the origins and dangerousness of properties.
An old intuition with generics is that at least some express properties that are especially enduring and central to a category [@Lyons1977]. 
This *principled connection* between a kind and a property supports both a normative expectation (e.g., *Ks should F*) and explanation of category membership [e.g., *x is a K because it Fs*; @Prasada2006].
@Gelman2007 posit that the way in which an exemplar comes to have a property---the *origins* of a property---can bring about a principled connection between the kind and the property. 
Learning that members of a category (e.g., *dobles*) are born with the property (e.g., born with claws) signals that the kind has a principled connection to the property, which is believed to be what makes the generic ("Dobles have claws") true.
By contrast, observing individuals who acquire the property from the external world (e.g., dobles who find claws on the side of the road and put them on) is less likely to bring about a principled connection, and the generic intuitively is less true. 

Further evidence for how our understanding of generics is tied to our conceptual knowledge comes from the observation that properties that are "striking, appalling, or otherwise gripping" make the generic "...more tolerant [...] to exceptions" [@Leslie2008; p.15].
This argument stems from an attempt to explain why sentences like "Mosquitos carry malaria" and "Tigers eat people" sound like true generic sentences despite the prevalence of the feature in the referent categories being exceptionally low. 
@Cimpian2010 provided empirical support for this claim using generics by testing adult intuitions about novel categories (e.g., "Lorches have dangerous purple feathers"). 
Information about the dangerousness of the property was found to increase participants' propensity to endorse generic sentences when information about the referent prevalence was fixed [e.g., when 30% of lorches have these purple feathers; @Cimpian2010, Expts. 1 & 4]. 

Both @Gelman2007 and @Cimpian2010 measure generic endorsement by having participants judge whether or the sentence is true or false (or, right vs. wrong).
In Chapter 3, we saw how endorsement depends on the referent prevalence (i.e., the prevalence of the property within the referent category) in a nonlinear, relative way that depends in turn on the distribution of prevalence of the property within a set of relevant alternative categories. 
Thus, the minimal computational model presented here already has two distinct mechanisms by which theory-based expectations can influence endorsement: the prevalence prior and the referent prevalence.
Prevalence prior distributions reflect complex structure (often manifesting as multi-modal distributions) and can change dramatically between properties of different types (e.g., biological vs. accidental properties; Ch. 2, Expt. 1; Ch. 3, Expt. 1, Expt. 2) and even within properties that are all of the same conceptual type (e.g., biological properties; Ch. 2, Expt. 2l Ch. 3, Expt. 2). 
Second, referent prevalence is not the objective frequency of the property among actual members of the category in the world, as is assumed in other studies.
Instead, the prevalence that matters for determining the truth or falsity of a generic is a subjective, predictive probability that exists in the mind of the speaker.
(Frequency information is relevant insofar as it informs a speaker's beliefs about the property or event's probability of occurring in the future.)
In our experiments on habitual endorsement (Ch. 3, Expt. 2c), we showed how endorsement patterns can easily be divorced from the objective, present frequency, even taking into account the prior distribution over prevalence.
In those experiments, participants' predictions about the future are what mediated their endorsement of habituals (though again, in a manner relative to the prevalence prior). 

We revisit the effects of property origins and property dangerousness through the computational lens of this dissertation.
First, if referent prevalence is what matters for generic endorsement, then the *pricipled connections* thought to result from learning intrinsic property origins in @Gelman2007 would matter only insofar as it increases the subjective probability that a future instance of the category would have the property. 
Second, if information about dangerousness is argued to influence generic endorsement in a way independent of prevalence, then it must be shown that information about dangerousness does not alter the prevalence prior.
We test these assumptions in this chapter.

We first replicate the effects shown in @Gelman2007 and @Cimpian2010 (Expt. 4).
We then design paradigms to measure the predictive prevalence and prevalence priors, respectively. 
We find that the endorsement patterns in these experiments can be accounted for by changes in the underlying prevalence representations that the generic endorsement model posits.

# Experiment 1: Property origins

So far, we have shown that property prevalence is sufficient to formalize the semantics of generic statements as an underspecified scalar denotation.
But what is property prevalence?
If generic language is truly conveying generalizations, it would be useful for it to reflect expectations, not just the current statistics in the world [cf., @Leslie2008].
The current frequency of a property is often a good indicator of future frequency, yet the statistics at any particular moment can be distorted by spurious events.
The causal history of a property should also be taken into account when determining whether the property will be present in future situations.
<!-- Does generic language communicate prevalence in terms of past frequency or future expectations? -->


@Gelman2007 found that adult endorsements of novel generics were sensitive to the origins of the property (i.e., whether or not the creatures were born with or acquired the property through extrinsic means).
In their paradigm, participants are told a story about a novel creature (e.g., dobles) and a property of that kind (e.g., have claws).
After being told the origins of the property (i.e., born with or found and put on), participants are told about an event that either causes the property to disappear (e.g., they drank a chemical and their claws fell off) or that leaves the property intact (e.g., they drank a yummy drink and felt happy).
The final display of the experiment shows the novel category in their current state: Dobles either with or without claws (depending on the outcome of the event).
Participants' judgments of the generic (e.g., "Dobles have claws") were *insensitive* to the current state (i.e., the outcome of the event, property maintained vs. lost): Participants fully-endorsed the generic when it was inborn, and rejected it when it was acquired.


In Experiment 1a, we use a paradigm similar to that of @Gelman2007 to replicate the effect of property origins on generic endorsement.
We replicate the effect of property origins, but also, unlike @Gelman2007, discover an effect of the current state.
In Experiment 1b, we alter the dependent measure to measure *predictive prevalence*: participants' expectations about future instances of the kind.
We find that, consistent with our hypothesis, predictive prevalence is altered by knowledge of the origins of the the property and tracks both the replicated main effect of property origins as well as the novel effect of current state.
Furthermore, predictive prevalence tracks with subtle item-level differences, further indicating that it is an intermediate representation between conceptual knowledge and generic endorsement.


## Experiment 1a: Endorsement task

The design of this experiment is based on a study reported in @Gelman2007 with slight modifications.

### Method

#### Participants

We recruited 80 participants over MTurk.  
The sample in @Gelman2007 was 14 undergraduates.
The experiment took about 3 minutes and participants were compensated \$0.35.
<!-- None of the participants completed Expt. 1b as well. -->

#### Procedure and materials

On each trial, participants read a vignette about a novel creature. For instance,

> These are dobles. [picture of ten dobles with claws] Here is how they grew. They grew up with claws. First they were born, then they got bigger, then they were full size. [picture of a doble with claws, getting bigger and bigger; in some vignettes, the animal was first shown hatching out of an egg with the relevant property already visible] Then one day they drank a bad chemical. They got very sick and this is how they looked. [picture of ten dobles without claws]

The trial proceeded by participants reading the text, and clicking a button to continue to the next part of the story (at which time, the images changed according to the example above).

Participants completed four trials: two in which the creatures are born with the property (*intrinsic origins*) and two in which the creatures are shown discovering and acquiring the property (*extrinsic origins* e.g., painting themselves brown).
Property origins were crossed with either the creatures drinking a "bad chemical" and losing the property, or drinking a "yummy drink" and maintaining the property.
The outcome of this event determined the final presentation of images that the participant saw (e.g., either ten dobles with claws or ten without).

With the final display of dobles present (either property lost or maintained), we measured endorsement by asking participants: "Do you agree or disagree that: *generic statement* (e.g., Dobles have claws)".
Participants responded by choosing one of two radio buttons corresponding to agree or disagree.

We used two different types of properties: colors (e.g., "Dobles are green.") and body parts (e.g., "Dobles have claws.").
For each type of property, there were approximately eight different property values (different colors or different body parts for different creatures).
The creatures were either birds, bugs, or fish, with randomly sampled physical dimensions (e.g., sizes of body or tail).
The experiment in full can be viewed at \url{http://stanford.edu/~mtessler/generics/experiments/predictive/predictive-1.html}.

#### Results

\red{ clean up }
<!-- %                                         Estimate Std. Error z value        Pr(>|z|)     -->
<!-- %(Intercept)                               -2.9444     0.5130  -5.740 0.0000000094624 *** -->
<!-- %event_outcomemaintained                    2.6931     0.5603   4.807 0.0000015342262 *** -->
<!-- %originsintrinsic                           3.6753     0.5658   6.496 0.0000000000824 *** -->
<!-- %event_outcomemaintained:originsintrinsic   0.2396     0.9400   0.255           0.799     -->

Our pragmatics model with the elicited predicted prevalence from Expt. 1a made two novel predictions for this experiment: (1) in addition to a main effect of origins, we would find a main effect of event outcome; (2) this effect would be stronger for body part properties than for color properties.

As predicted, we found two main effects (Figure \ref{fig:dobles}b, top).
The main effect of property origins replicated ($\beta=3.6, SE=0.57, z=6.5, p<1\text{e}10$): participants were more likely to endorse the generic when it was about a property that the creature was born with.
In addition, we find a second main effect of event outcome 
 ($\beta = 2.69, SE = 0.56, z=4.8, p<1\text{e}5$): participants were more likely to endorse the generic when the property was maintained than when it was lost.
 
The fact that we find a second main effect of event outcome in addition to origins, whereas the original only found a main effect of origins, makes it worth noting the differences between our paradigm and the original study by [@Gelman2007].
In the original study, the first sentence of each vignette used the possessive "my": "These are my dobles.".
At the end of each vignette, the original study had participants judge two statements in counterbalanced order: "Do my dobles have claws?" and "Do dobles have claws?"
Finally, the original sample size was 14; ours was 80. 
To see whether this second main effect could be attributed to a subgroup of participants making their judgments based only on the final screen (which showed creatures with or without the property, depending on the event outcome), we classified each participant according to their pattern of responses. 
Just as many participants endorsed the generic based on the final screen alone (*Only outcome*: 19) as there were basing their endorsement on both the outcome and the origins (*Both outcome and origins*: 16).
36 participants based their responses on only the origins, and 9 participants exhibited some other pattern of responses.
Thus, it seems this effect is not due to a subgroup of participants basing their responses on only the final screen.

\begin{table}[]
\centering
\begin{tabular}{@{}lllll@{}}
\toprule
  & Only origins & Only outcome & Both & Neither \\ \midrule
n & 36           & 19           & 16   & 9       \\ \bottomrule
\end{tabular}
\caption{Numbers of participants ($N=80$) who made their generic endorsement based on different factors.}
\label{tab:dobles}
\end{table}


When we break down the results by item, we see that this effect is stronger for body part properties than for color properties (Figure \ref{fig:dobles}b, bottom).
The endorsement of a generic for color properties (e.g., "Lorches are green") seems to be less sensitive to the outcome of the event (i.e. Lorches losing their color as a result of drinking a chemical).
This may be due to participants' intuitive theories of properties and their stability (skin color is more stable than body parts like feathers).

\begin{figure*}
\begin{tabular}{l l}
(a) $S_2$ model predictions & (b) Human endorsement of generic statements \\
\\
\centering
    \includegraphics[width=0.5\columnwidth]{figs/dobles-model.pdf} &
        \includegraphics[width=0.5\columnwidth]{figs/dobles-results.pdf} \\
      \includegraphics[width=0.5\columnwidth]{figs/dobles-model-byItem.pdf} &
      \includegraphics[width=0.5\columnwidth]{figs/dobles-byItem-results.pdf} \\
\end{tabular}
    \caption{
    Prevalence is a predictive probability.
    (a) Truth judgment model predictions given the predicted prevalence elicited in Expt.~3a.
    (b) Average endorsement of the generic statement in Expt.~3b (replication of Gelman and Bloom, 2007).
    Bottom row shows data and predictions broken down by property type.
  }
  \label{fig:dobles}
\end{figure*}

```{r doblesResults, eval =F}
fig.dobles.1 <- ggdraw() + draw_image("figs/dobles-model.pdf", scale = 1) +
  theme(plot.margin = unit(c(2,0,0,0), "pt"),
        panel.background = element_rect(colour = "black", size=1)) 
fig.dobles.2 <- ggdraw() + draw_image("figs/dobles-results.pdf", scale = 0.9)+
  theme(plot.margin = unit(c(2,0,0,0), "pt"),
        panel.background = element_rect(colour = "black", size=1)) 
fig.dobles.3 <- ggdraw() + draw_image("figs/dobles-model-byItem.pdf", scale = 0.95)+
  theme(plot.margin = unit(c(2,0,0,0), "pt"),
        panel.background = element_rect(colour = "black", size=1))
fig.dobles.4 <- ggdraw() + draw_image("figs/dobles-byItem-results.pdf", scale = 0.95)+
  theme(plot.margin = unit(c(2,0,0,0), "pt"),
        panel.background = element_rect(colour = "black", size=1))

plot_grid(
  fig.dobles.1,
  fig.dobles.2,
  fig.dobles.3,
  fig.dobles.4,
  nrow = 2
)
```

## Experiment 1b: Predictive prevalence elicitation

In this experiment, we test the prediction that the effect of property origins and current state observed in Expt. 1a can be explained by differences in participants' predictions about the property in future instances of the category.

### Method

#### Participants

We recruited 80 participants over MTurk.  
The experiment took about 3 minutes and participants were compensated \$0.35.

#### Procedure and materials

The procedure and materials are exactly the same as in Expt. 1a, with the exception of the dependent measure.
After reading the vignette and being shown the final screen of exemplars, we measured *predictive prevalence* by telling participants: "A new doble was born today. When it becomes full grown, how likely is it that it would *have property* (e.g. have claws)?"
Participants responded using sliders ranging from "very unlikely" to "very likely".

### Results and truth judgment predictions

The computational model predicts that generic endorsement is modulated by a speaker's degree of belief in the property being present in future instances of the category. 
In order to evaluate this hypothesis, we subjected the predicted prevalence data to a mixed-effects regression model with random by-item, and random by-participant ...

<!-- The average predicted prevalences for the four experimental conditions are shown in Table \ref{tab:predictive}. -->
<!-- We observe a main effect of origins, such that when participants read that the creatures had the property from birth, future creatures  are much more likely to have the property as compared to when the property is acquired. -->
<!-- We see that, in our paradigm, participants are also sensitive to the outcome of the event  (property lost or maintained). -->
<!-- This is surprising given @Gelman2007's reporting of no effect of the event outcome on endorsement. -->
<!-- When participants observe a creature who loses the property by drinking a chemical, they report future members of the category are less likely to have the property. -->
<!-- This inference could be driven by inferences about the property (e.g., learning that the property is an unstable property because you can lose it simply by drinking something) or by inferences about the event (e.g., learning that the "chemical drinking" event is within the space of possibilities for dobles, and thus it could happen in the future). -->

The computational model's predictions are not necessarily the same as the predicted prevalence values, but instead depend upon the listener's prevalence prior distribution. 
Since the properties are only of two types (color and body part) and both biological in nature, we do not expect substantial interactions with the prevalence prior; futher, since the priors for body part and color priors elicited in Ch. 2. (Expt. 1a) are both relatively broad (high variance), we expect predicted generic endorsement to track predictive prevalence to a large degree.
We use these predicted probabilities as the referent prevalence $p$ that the speaker model is trying to communicate: $S(u\mid p)$, and examine the model's predicted endorsments, using the body part and color priors elicited in Ch. 2. (Expt. 1a) as the priors in this model.
The model predictions track closely with the predicted prevalence (Figure \ref{fig:dobles}a, top, compare with predicted prevalence in Table \ref{tab:predictive}), and thus with the empirical generic endorsement (Expt. 1a). 
<!-- Indeed this difference is apparent in the predictive prevalence task (Expt. 1a). -->
For the eight data points of generic endorsement based on origins, outcome, and property type, our model's predictions match the data well ($r^2(8) = 0.96$).
<!-- We, thus, elaborate our theory: -->
The semantics of generics can be understood as a threshold on property prevalence, and this prevalence is a speaker's subjective belief about what is likely to be the case in the future.


<!-- This is because both color and body part priors are relatively broad, and hence when the property is (predicted to be) more prevalent, the generic has a higher probability of applying (see schematic predictions from Figure \ref{fig:schematic-unif} ``have wings'' for comparison). -->
<!-- We also see that the model predicts a subtle by-item difference, such that the influence of the event outcome (lost or maintained) on generic endorsement is predicted to be stronger for body parts than for color terms (Figure \ref{fig:dobles}a, bottom). -->
<!-- This prediction is mostly due to the predicted prevalence for the conflict conditions (intrinsic-lost and extrinsic-maintained) being subtly different (Table \ref{tab:predictive}, right-most columns). -->



\begin{table}
\centering
\begin{tabular}{l|l|r|r|r}
\hline
Origins & Event Outcome & Collapsed Mean [95\% CI]  & Color  [95\% CI] & Body Part [95\% CI] \\
\hline
Extrinsic & Lost  & 0.15 [0.10, 0.21]& 0.13 [0.07, 0.21] & 0.17 [0.09, 0.26] \\
\hline
Extrinsic & Maintained & 0.32 [0.24, 0.39] & 0.24 [0.16, 0.35] & 0.38 [0.27, 0.50] \\
\hline
Intrinsic & Lost  & 0.69 [0.62, 0.76] & 0.73 [0.63, 0.83] & 0.66 [0.56, 0.75] \\
\hline
Intrinsic & Maintained  &0.95 [0.94, 0.97] & 0.96 [0.94, 0.98] & 0.94 [0.91, 0.97] \\
\hline
\end{tabular}
\caption{Predicted prevalence for the four experimental conditions of Expt.~3a. Right two columns show the summaries broken down by the two types of properties used in the experiment.}
\label{tab:predictive}
\end{table}

<!-- We use these predicted probabilities as the prevalence $p$ that the speaker model is trying to communicate: $S(u\mid p)$, and examine the model's predicted truth judgments. -->
<!-- We explore the model's predictions for each origin and event outcome, as well as when the data is split by property type (color vs. body parts).  -->
<!-- For priors $P(p)$, we use the body part and color priors elicited in Ch. 2., Expt. 1a. -->
<!-- We see that the model predictions track closely the predicted prevalence (Figure \ref{fig:dobles}a, top, compare with predicted prevalence in Table \ref{tab:predictive}). -->
<!-- This is because both color and body part priors are relatively broad, and hence when the property is (predicted to be) more prevalent, the generic has a higher probability of applying (see schematic predictions from Figure \ref{fig:schematic-unif} ``have wings'' for comparison). -->
<!-- We also see that the model predicts a subtle by-item difference, such that the influence of the event outcome (lost or maintained) on generic endorsement is predicted to be stronger for body parts than for color terms (Figure \ref{fig:dobles}a, bottom). -->
<!-- This prediction is mostly due to the predicted prevalence for the conflict conditions (intrinsic-lost and extrinsic-maintained) being subtly different (Table \ref{tab:predictive}, right-most columns). -->

<!-- The model thus makes two novel predictions for generic endorsement in the paradigm by @Gelman2007. -->
<!-- We predict that in addition to the main effect of origins, we should see a second main effect of event outcome. -->
<!-- Second, we predict that this effect should be slightly stronger in the case of color properties than in the case of body part properties. -->

<!-- ## Discussion -->




# Experiment 2: The impact of strikingness

@Leslie2007 brings our attention to examples like the following:

1. Sharks attack bathers.
2. Rottweilers maul children. 
3. Mosquitos carry the West Nile Virus.

In each case, the property is somehow *striking, alarming,* or *dangerous*:

> The examples... have something in common: In all of them, the sentence attributes harmful, dangerous, or appalling properties to the kind. More generally, if the property in question is the sort of property of which one would be well served to be forewarned, even if there were only a small chance of encountering it, then generic attributions of the property are intuitively true. (2008, p.15)

@Leslie2008 argues that these generics are reasonable utterances, even though the actual prevalence of the property is quite low (e.g., less than 1% of mosquitos carry the West Nile Virus), because the property is *striking*. 
@Cimpian2010 (Expt. 1) found that generics about novel categories (of the kind seen in Chapter 4) are endorsed more highly when the property being predicated is *distinctive and dangerous*. 
In a follow-up (Expt. 4), the increase in endorsement was found for properties that were described independently as either distinctive or dangerous.

The information-theoretic communicative model predicts that these differences in endorsements are mediated by corresponding differences in the prevalence prior distributions. 
Indeed, we have already seen in Chapter 3 (generic endorsement) that statements about familiar categories like Sentences 1-3 are endorsed despite low referent prevalence because the prevalence prior distribution reflects that of a distinctive property.
That is, because most animals do not carry the West Nile Virus, and even among those that do, the prevalence is quite low, the endorsement model is willing to assert the generic sentence even though very few mosquitos carry the West Nile Virus. ^[
  An alternative possibility, still within the space of our endorsement model and one that @Leslie2008 suggests, is that a speaker's perception of the prevalence of the feature is altered by virtue of its dangerousness [@Rothbart1978].
  This explanatory mechanism would be the same as the one we explored in Expt. 1.
]

Here, we examine if the relationship between striking or dangerous properties and prevalence priors also holds for generics about novel  categories using the set of dangerous items used by @Cimpian2010. 
We reverse the order of our standard experimental procedure.
First, we replicate the findings of @Cimpian2010 Expt. 4, to try to find the influence of dangerousness information on generic endorsement.
Then, we run a prior elicitation paradigm and use our computatoinal model to jointly model both sets to see if these differences in endorsements can be traced back to differences in the prevalence prior distributions. 

## Experiment 2a: Truth judgment task

This experiment is a replication of @Cimpian2010 Expt. 4. 

### Method

#### Participants

We recruited 40 participants over MTurk. 
The experimental design is very similar to @Cimpian2010 (Expt. 4), and we chose to have a sample size at least twice as large as the original study (original n=15). 
All participants were native English speakers. 
The experiment took about 5 minutes and participants were compensated \$0.60.

#### Materials

The materials were taken from @Cimpian2010 (Expt. 4).
Properties were either described as dangerous, distinctive, or neither. 


#### Procedure

In order to get participants motivated to reason about novel kinds, they were told they were the resident zoologist of a team of scientists on a recently discovered island with many unknown animals; their task was to provide their expert opinion on questions about these animals.
On each trial, participants were given a statement about a property's prevalence within a novel kind (*referent prevalence*; e.g. "50% of feps have yellow fur."). 
Participants were then asked whether or not they agreed or disagreed with the corresponding generic sentence (e.g. "Feps have yellow fur.").
Referent prevalence varied between 10, 30, 50, 70, and 90%.

The experiment consisted of thirty trials. Participant saw each prevalence level twice paired with each of the three kinds of property (5 prevalence levels x 2 repetitions x 3 property types).

### Results

## Experiment 2b: Prior elicitation

### Method

#### Participants

We recruited 40 participants over MTurk. 
All participants were native English speakers. 
The experiment took about X minutes and participants were compensated \$Y.

#### Materials and procedure

The experiment was divided into two blocks. 
In the first block, participants were told that on this island there were one thousand (1000) different species of animals. They were asked to make a prediction about how many different species of animals they thought would have the property.
In the second block, participants were told they scientists came across a particular instance of a novel category with the property (e.g., "Scientists today saw a glippet. It had *property*") and asked to predict how many other instances of the category had the property (e.g., "What percentage of other glippets do you think *have property*?").


The materials were the same as in Expt. 2a. 

### Results

<!-- # Experiment 3: Transient properties -->

# Discussion

## Predictive prevalence and sufficiently long histories

- report on pilot data (n = 15 each):
  - If you were to encounter another doble, how likely is it that it would have claws?
  - There are 100 other dobles on the planet. How many of them do you think have claws?
  - Predictive born today
  - Predictive other side of planet

- relation to "normal" generics approaches

<!-- 

- dangerousness also distorts predictive prevalence?
  - Leslie draws on inspiration about people's predictions about the likelihood of encountering a dangerouesness property (Leslie  2008, Rothbart etal 1978).
  - Also, representativeness heuristic (KT) in bringing rare events to mind.  
  
- does dangerousness infleunce generic understanding beyond rational(ish) probabilities? 
  - the evidence that dangerounsness impacts endorsement is confounded... there is no evidence that dangerousness impacts endorsements outside of the relevant probabilities 
  - Sterken 2015 argues that these statements are false assertions
  - "loose talk" theories
  - what does Leslie have to say about the mechanisms by which dangerous information is connected?
  - Prasada descrbies the "causal connections"
    - is there a difference between "causal" and "principled" connections in our model? (no, the model is agnositc... also no difference for "statistical" connections...)
-->

\newpage

# References


```{r create_r-references}
r_refs(file = "generics.bib")
```

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
